---
title: "Influence of top 100 director on average director rating"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Introduction

The following ANOVA table provides an answer to research question 3: To what extend does beıng a top 100 dırector or not ınfluence average ratıng, and how does the amount of revıews ınfluence thıs relatıonshıp?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
tinytex::install_tinytex(force = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
df <- read_csv("../../gen/data_preparation/output/pivot_table.csv")
```

```{r message=FALSE, warning=FALSE}
model_anova <- lm(avg_director_rating ~ top_100 * avg_num_votes, data = df)
anova_result <- anova(model_anova)
print(anova_result)
```

# Explanation

As is visible from the ANOVA all paths are significant (P<0.05). This means that the average director rating is higher for directors in the top 100 list compared to directors not in that list. In addition, the number of votes a director compiles also leads to an increase in the average rating a director receives. Finally, the ANOVA shows that there is an interaction effect. Which means that .... (needs to be figured out).
